### 2023-04-02 output/group_0_crimes_100m/tables/balance_table.tex
edited merge script

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 7.20 & 0.54 & 0.04 & -0.05 & 0.83 \\
 & pre_treatment_change_in_group_2_crimes_100m & 0.03 & -0.03 & 0.13 & -0.00 & 0.95 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.00 & 0.68 \\
 & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -429.96 & 0.60 \\
 & poor_share2010 & 0.27 & -0.00 & 0.53 & -0.00 & 0.57 \\
 & popdensity2010 & 23,086.04 & 1,225.15 & 0.01 & -185.35 & 0.65 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & isEntityD & 0.01 & -0.01 & 0.01 & -0.00 & 0.90 \\
 & isEntityP & 0.81 & -0.06 & 0.00 & -0.01 & 0.30 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_4_crimes_100m & 1.67 & -0.05 & 0.74 & -0.07 & 0.62 \\
 & pre_treatment_change_in_group_4_crimes_100m & -0.02 & -0.00 & 0.87 & 0.00 & 1.00 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.00 & 0.78 & -0.01 & 0.11 \\
 & job_density_2013 & 16,069.14 & 926.91 & 0.52 & -234.26 & 0.87 \\
 & med_hhinc2016 & 48,035.65 & 1,312.56 & 0.12 & -1,185.57 & 0.00 \\
\cline{1-7}
\textit{Panel D} & isEntityP & 0.81 & -0.06 & 0.00 & -0.05 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-02 output/group_0_crimes_100m/tables/pre_treatment_covariate_tests.tex
edited merge script

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.13 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
 & job_density_2013 & 0.75 & 0.52 \\
 & med_hhinc2016 & 0.00 & 0.12 \\
 & poor_share2010 & 0.03 & 0.53 \\
 & popdensity2010 & 0.00 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.28 & 0.00 \\
 & no_cause & 0.45 & 0.90 \\
 & non_payment & 0.22 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.28 & 0.00 \\
 & hasAttyP & 0.21 & 0.00 \\
 & isEntityD & 0.00 & 0.01 \\
 & isEntityP & 0.01 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.74 \\
 & pre_treatment_change_in_group_4_crimes_100m & 0.00 & 0.87 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.78 \\
 & job_density_2013 & 0.00 & 0.52 \\
 & med_hhinc2016 & 0.00 & 0.12 \\
 & poor_share2010 & 0.24 & 0.53 \\
 & popdensity2010 & 0.18 & 0.01 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.21 & 0.00 \\
 & no_cause & 0.52 & 0.90 \\
 & non_payment & 0.16 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
 & hasAttyP & 0.26 & 0.00 \\
 & isEntityD & 0.63 & 0.01 \\
 & isEntityP & 0.03 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}
